---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo = FALSE, message= FALSE}
knitr::opts_chunk$set(collapse = T, comment="#>")
library(binomial)
library(ggplot2)
```
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

# Binomial

`"binomial"` is a self-created R package that implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, and expected value, variance, etc.

### 1) Calculate the number of different combinations given certain number of trials and successes.

for example, we play 5 times and expect 2 successes
```{r}
bin_choose(n=5,k=2)
```

### 2) Find the probability given certain number of trials and successes

We generate the bin_probability function using bin_choose function above. Using the functions below, we can calculate the probability of winning 2 times in 5 trials with success probability of 0.5 for each single trial.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

### 3) obtain a dataframe given certain number of trials and successes

Using given number of trials and successes, we can obtain a data frame containing all the results(probability) corresponding to consequtive number of trials from 0 to the given number of trials

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
```

### 4) Plot the histogram of above dataframe

```{r}
plot(dis1)
```

### 5) Calculate the cumulative probability

Using given number of trials and successes, we can obtain a data frame containing all the results(probability and cumulative probability) corresponding to consequtive number of trials from 0 to the given number of trials
```{r}
bin_cum<- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
```

### 6) Plot the cumulative probability

plot the bin_cum we obtained above.
```{r}
plot(bin_cum)
```

### 7) Create binomial variable using given number of trials and successes

```{r}
bin_var <- bin_variable(trials=5,prob=0.5)
bin_var
```

### 8) Obtain a summary of binomial variable above

```{r}
bin_sum <- summary(bin_var)
bin_sum
```

### 9) Calculate several statistics of binomial variable above

`bin_mean` gives the mean of given binomial distribution.    
`bin_variance` gives the variance of given binomial distribution.    
`bin_mode` gives the mode of given binomial distribution.         
`bin_skewness` gives the skewness of given binomial distribution.        
`bin_kurtosis` gives the kurtosis of given binomial distribution.  

```{r}
bin_mean(10,0.5)
bin_variance(10,0.5)
bin_mode(10,0.5)
bin_skewness(10,0.5)
bin_kurtosis(10,0.5)
```



